---
title: "Azure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Azure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Getting Started

```{r setup}
library(unifrog)

```

1. Ensure you are connected to any required VPNs

2. Run `setupAzureCreds()`. You'll be prompted to enter the server, database, username and password. They will be securely stored in your operating system's credential manager.


3. To update credentials use `updateAzureCreds()`. This will prompt you for the fields that change.

### Getting results from Azure database.

The `getAzureResults()` function is able to query the database, so long as you are connected to the VPN. 

By default, the query results are also stored as a .parquet file in the data directory.

In the example below, data/query_name.parquet already exists and so no query will be executed. Instead, the .parquet file will be read in using `arrow::read_parquet()`
```{r example1}
query <- "queries/query_name.sql"
results <- getAzureResults(
  SQLscript = query
)
results
```

The default behaviour can be overridden if, for example, the data or query has changed by using the `overwrite = TRUE` argument.
```{r example2, eval=FALSE}
results <- getAzureResults(
  SQLscript = query,
  output = "data/query_name.parquet",
  overwrite = TRUE
)
results
```

Sometimes, you might want to change the query before passing to the function. In this case the raw `.sql`query must first be formatted using helper functions from `glue` and `readr`. In the example below we first read in the sql script.

```{r read}
library(readr)
query_text <- read_file("queries/query_name.sql")
query_text
```
Next we modify the script.
```{r str_replace}
library(stringr)
modified <- query_text |> 
  str_replace("student_year_of_graduation", "student_school")
modified
```
The script must be 'glued' before passing to the function.
```{r glue}
library(glue)
query <- glue_sql(modified)
query
```

```{r example3}
results <- getAzureResults(
  SQLscript = query,
  output = "data/query_results2.parquet",
  glued = FALSE
)
results
```
