---
title: "Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Palettes}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggplot2)
library(forcats)
library(unifrog)
```

### Unifrog Colors

This extracts the unifrog palette colours as hex codes. Examples below.

```{r unifrog_colors}
unifrog_colors()
```

```{r unifrog_colors_specified}
unifrog_colors("green", "teal", "darkgrey")
```

#### unikn

You can view the palettes in a pretty way using the `unikn` package

```{r}
library(unikn)
seecol(unifrog_colors(), main = "The entire Unifrog colour scheme")
```

```{r}
seecol(qual_vibrant, main = "The \"qual_vibrant\" palette is default for discrete data")
```

```{r}
seecol(seq_iridescent, main = "The \"seq_iridescent\" palette is default for continuous data")
```

```{r}
seecol(cb_palettes,
  main = "The names of all of the Unifrog palettes",
  pal_names = names(cb_palettes)
)
```

They have been grouped in three colour-blind friendly categories:

Discrete - 'qual_bright', 'qual_vibrant', 'qual_hc', 'qual_muted', 'qual_mc', 'qual_pale', 'qual_light'

Sequential - 'seq_YlBr', 'seq_iridescent', 'seq_incandescent'

Diverging - 'div_sunset', 'div_nightfall', 'div_PrGn', 'div_BuRd'

### scale_fill_unifrog

If no fill is specified, for a categorical variable, then the default is `scale_fill_unifrog_d("qual_vibrant")`.

```{r}
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_boxplot() +
  theme_classic()
```

You can see that the addition of line 4 has no effect on the output

```{r}
#| code-line-numbers: true
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_unifrog_d()
```

Addition of `reverse = TRUE` on line 4 starts from the opposite end of the palette.

```{r}
#| code-line-numbers: true
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_unifrog_d(reverse = TRUE)
```

In order to guarantee the colour reversal for `qual_vibrant` use `fct_rev` in the fill argument.

```{r}
#| code-line-numbers: true
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = fct_rev(Species))) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_unifrog_d()
```

If you want to use a different palette, you can specify it with the palette argument.

::: callout-note
Note a sequential palette does not often make sense for bar charts.
:::

```{r}
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_violin() +
  scale_fill_unifrog_d(palette = "div_PrGn") +
  theme_classic()
```

### scale_color_unifrog

For continuous variables, the default is `scale_fill_unifrog_c("seq_iridescent")`

```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = hwy)) +
  geom_point() +
  unifrog_theme(axis = TRUE)
```

You can change this the same way as shown above but using the color aesthetic.

```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = hwy)) +
  geom_point() +
  scale_color_unifrog_c("likert3") +
  unifrog_theme()
```
