---
title: "Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggplot2)
library(forcats)
library(unifrog)
```

### Unifrog Colors

This extracts the unifrog palette colours as hex codes. Examples below.

```{r unifrog_colors}
unifrog_colors()
```

```{r unifrog_colors_specified}
unifrog_colors("green", "lightblue", "darkgrey")
```

#### unikn

You can view the palettes in a pretty way using the `unikn` package

```{r}
library(unikn)
seecol(unifrog_colors(), main = "The entire Unifrog colour scheme")
```

```{r}
seecol(unifrog_main, main = "The \"main\" palette is default for discrete data")
```

```{r}
seecol(likert3, main = "The \"likert3\" palette is default for continuous data")
```

```{r}
seecol(unifrog_palettes,
       main = "The names of all of the Unifrog palettes",
       pal_names = names(unifrog_palettes))
```

They have been grouped in three categories:

Discrete - 'unifrog_main'

Sequential - 'unifrog_blues', 'unifrog_greens', 'unifrog_oranges', 'unifrog_reds'

Diverging - 'likert3', 'likert5', 'likert7'

### scale_fill_unifrog

If no fill is specified, for a categorical variable, then the default is `scale_fill_unifrog_d("unifrog_main")`.

```{r}
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_boxplot() +
  theme_classic()
```

You can see that the addition of line 4 has no effect on the output

```{r}
#| code-line-numbers: true
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_unifrog_d()
```

Addition of `reverse = TRUE` on line 4starts from the opposite end of the palette.

```{r}
#| code-line-numbers: true
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_unifrog_d(reverse = TRUE)
```

In order to guarantee the colour reversal for `unifrog_main` use `fct_rev` in the fill argument.

```{r}
#| code-line-numbers: true
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = fct_rev(Species))) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_unifrog_d()
```

If you want to use a different palette, you can specify it with the palette argument.

::: callout-note
Note a sequential palette does not often make sense for bar charts.
:::

```{r}
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_violin() +
  scale_fill_unifrog_d(palette = "unifrog_greens") +
  theme_classic()
```

### scale_color_unifrog

For continuous variables, the default is `scale_fill_unifrog_c("likert3")`

```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = hwy)) +
  geom_point() +
  theme_bw()
```

You can change this the same way as shown above but using the color aesthetic.

```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = hwy)) +
  geom_point() +
  scale_color_unifrog_c('likert5') +
  theme_bw()
```
